---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- From this tutorial: https://towardsdatascience.com/getting-r-and-d3-js-to-play-nicely-in-r-markdown-270e302a52d3 -->

```{r data-var-R}
head(cars)
```

###### ***\*\*you have to include the results="asis" option in the curly braces at the top of the code chunk to pass the data through\*\****

```{r vectors-to-json, echo=FALSE, results="asis"}
library("jsonlite")
cat(
  paste(
  '<script>
    var data = ',toJSON(cars),';
  </script>'
  , sep="")
)
```

<!-- Load the D3 library -->
<script src="https://d3js.org/d3.v4.min.js"></script>

<!-- Code for visualization -->
<div id="plot"></div>

<script>

// set the dimensions and margins of the graph
var margin = {top: 20, right: 20, bottom: 30, left: 50},
    width = 900 - margin.left - margin.right,
    height = 500 - margin.top - margin.bottom;

// set the ranges
var x = d3.scaleLinear().range([0, width]);
var y = d3.scaleLinear().range([height, 0]);

// append the svg object to the body of the page
// appends a 'group' element to 'svg'
// moves the 'group' element to the top left margin
var svg = d3.select("#plot").append("svg")
    .attr("width", width + margin.left + margin.right)
    .attr("height", height + margin.top + margin.bottom)
  .append("g")
    .attr("transform",
          "translate(" + margin.left + "," + margin.top + ")");


// format the data
data.forEach(function(d) {
    d.speed = +d.speed;
    d.dist  = +d.dist;
});

// Scale the range of the data
x.domain(d3.extent(data, function(d) { return d.speed; }));
y.domain([0, d3.max(data, function(d) { return d.dist; })]);

// Add the scatterplot
svg.selectAll("dot")
    .data(data)
  .enter().append("circle")
    .attr("r", 5)
    .attr("cx", function(d) { return x(d.speed); })
    .attr("cy", function(d) { return y(d.dist); });

// Add the X Axis
svg.append("g")
    .attr("transform", "translate(0," + height + ")")
    .call(d3.axisBottom(x));

// Add the Y Axis
svg.append("g")
    .call(d3.axisLeft(y));

</script>